Community-Conditioned Language Models

### 2021-05-14 paper/paper.tex
a couple of cclm embedding things

To this end, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them using using a negative-sampling optimization
algorithm and the message-community co-occurrence matrix as ground
truth, using data which spans January 2014 to April 2017.
We refer the reader
to \citet{Kumar2018}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data.
%

@@

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have computed experimentally \(d(L,S)\) for 
\(L\) and \(S\) chosen at random and 16 dimensions. We find
a mean of TODO and a standard deviation of TODO.

Thus \(d(L,S)\) below \(μ-3σ\) can be safely considered to indicate a
statistically significant correlation between \(L\) and
\(S\). However, below, we will also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\).

>>>>

To this end, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them using using a negative-sampling optimization
algorithm and the message-community co-occurrence matrix as ground
truth, using data which spans January 2014 to April 2017.
We refer the reader
to \citet{Kumar2018}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether a given user participates in a given
community. In sharp contrast, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data.
%

@@

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have computed experimentally \(d(L,S)\) for 
\(L\) and \(S\) chosen at random and 16 dimensions. We find
a mean of \num{73.83} and a standard deviation of \num{1.89}.

Thus \(d(L,S)\) below \(μ-3σ\) (\num{68.15}) can be safely considered to indicate a \bn{above  \(μ+3σ\) (\num{79.50})?}
statistically significant correlation between \(L\) and
\(S\). However, below, we will also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\).
